\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5} % For professional icons

% Define Stellenbosch Maroon
\definecolor{MatiesMaroon}{HTML}{7D2128}
\definecolor{TextDark}{HTML}{2D2D2D}

% Global Font - Modern Sans-Serif
\usepackage[sfdefault]{inter} 
\usepackage[T1]{fontenc}

% Header Formatting
\hypersetup{colorlinks=true, urlcolor=MatiesMaroon}

% Section Formatting
\titleformat{\section}{\large\bfseries\color{MatiesMaroon}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{14pt}{10pt}

% List Formatting
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.2em}

% footnote formatting
\usepackage[bottom]{footmisc}

\begin{document}
\pagestyle{empty}
\color{TextDark}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{CARLO SMIT}} \\
    \vspace{6pt}
    \small
    \faMapMarker* Cape Town, South Africa \quad 
    \faPhone \ 061 260 0207 \quad 
    \faEnvelope \
	\href{mailto:carlo.smit23@outlook.com}{carlo.smit23@outlook.com} \quad
 \faEnvelope \href{mailto:27858308@sun.ac.za}{27858308@sun.ac.za} \\
    \vspace{2pt}
    \faGithub \ \href{https://github.com/Carlo-J-Smit}{github.com/Carlo-J-Smit} \quad 
    \faLinkedin \
	\href{https://www.linkedin.com/in/carlo-smit-a435a0332/}{linkedin.com/in/carlo-a435a0332}
\end{center}

% --- Summary ---
\section{SUMMARY}
I'm a 21 year old Computer Science graduate student with a passion for
computing, problem solving and engineering. I pride myself in trying to achieve
the most efficient solution and like the thrill of solving problems and
building a solution that people can use. Since I was a child,
I've had an interest in STEM and have undertaken hobbies to expand my analytical
and problem solving skills. I am an extremely hard worker, and often finishes my
projects multiple weeks before their deadlines. I was raised to respect the time
of others and to respect my own work and, therefore, I always do more than what is
expected from me. I am excited and eager to start building my life long career
and expanding my knowledge by learning from mentors and industry experts.

% --- EDUCATION ---
\section{EDUCATION}
\textbf{Stellenbosch University} \hfill Stellenbosch, SA \\
\textit{BSc in Computer Science} \hfill \textbf{Expected Dec 2026}

	\vspace{5pt}


\begin{itemize}
	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
	\item \textbf{Mark to date:} 75.357 \% as of this month\footnote{This refers
			to the average
			of the recognized modules as outlined by the Faculty of Science 
			Yearbook and the granted concessions for BSc Computer Science 
			(General Focus). It excludes modules completed under the Data 
			Science focus.}
	\renewcommand{\thefootnote}{\arabic{footnote}}
	
	\vspace{2pt}


	\item \textbf{Specialization:} While I am currently studying general
		Computer Science, I spent 2 years of the 3 studying towards a focus of
		Data Science and thus have a strong background in Data Science and
		Statistics.
		
	\vspace{2pt}


	\item \textbf{Excel Award:} The Excel Award is allocated to the top 1 to 5\%
		of first-time entry, first-year registered students per faculty.

\end{itemize}


\vspace{8pt}
\hrule
\vspace{8pt}

\noindent \textbf{Durbanville Ho\"{e}rskool} \hfill Durbanville, SA \\
\textit{National Senior Certificate} \hfill \textbf{2023}

\vspace{5pt}
\noindent \textbf{Subjects:} 89.857\% average
\vspace{2pt}

\begin{description}[style=multiline, leftmargin=10cm, font=\normalfont\color{TextDark}]
	\item[Afrikaans Home Language] 84\%
	\item[English Home Language] 86\%
	\item[Mathematics] 88\%
	\item[Life Orientation] 91\%
	\item[Engineering Graphics and Design] 98\%
	\item[Information Technology] 97\%
	\item[Physical Sciences] 85\%
\end{description}

\vspace{2pt}
\textbf{Notable Achievements:}
\vspace{2pt}

\begin{itemize}
	\item Subject and Academic Prizes: 
		\begin{itemize}
	\item Engineering Graphics and Design - best in year | 2021 - 2023
	\item Top 15 Academically - per year | 2021 - 2023
	\end{itemize}
	\item Leadership: Captain for my grade 12 rugby team
\end{itemize}


% --- TECHNICAL SKILLS ---
\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Languages:} Java, Python, C, SQL.
		
	\vspace{2pt}


    \item \textbf{Tools \& Frameworks:} JavaFX, Pandas, NumPy, Scipy, Simpy, Matplotlib,
		Seaborn, Git, Tailscale, Blender, neo vim, vs code, \LaTeX.
		
	\vspace{2pt}


    \item \textbf{Environments:} Ubuntu Linux, Windows.
		
	\vspace{2pt}


    \item \textbf{Core skills:} Prescribed Stellenbosch University BSc Computer
		Science curriculum, Data analysis, interpretation and visualisation,
		exposure and basic knowledge of dart, firebase and google cloud. Basic
		modeling and rendering knowledge (hobby)
\end{itemize}

% --- TECHNICAL PROJECTS ---
\section{TECHNICAL PROJECTS}

\textbf{StelliesLive} \hfill \textit{Dart, Flutter, Firebase}

	\vspace{5pt}


\begin{itemize}
	\item \textbf{Description:} During my free time I played around with and investigated the workflow
		and ability of LLM chat agents and their ability to code and a coherent
		app capable and worthy of releasing it to the public. My full
		conclusions can be found in the README on my GitHub profile. 
		\href{https://github.com/Carlo-J-Smit/stelliesLive}{stelliesLive}

	\vspace{2pt}

	\item \textbf{Tech Stack:} The app was coded in dart on the flutter
		framework in order to build to multiple platforms without having to
		recode sections. Google's firebase features was used throughout the app,
		including but not limited to authentication, Firestore and cloud
		functions.

\end{itemize}

\vspace{8pt}

% --- EXPERIENCE ---
\section{EXPERIENCE}
\textbf{Manual Labour} | \textit{Rhodes Food Group - Juice Plant factory shop}
\hfill Nov 2024 -- Dec 2024

	\vspace{5pt}


\begin{itemize}
	\item \textbf{Description:} Worked as a general labourer in the factory shop
		and warehouse, packing shelves and orders, as well as helping customers.

	\vspace{2pt}


	\item \textbf{Skills learned:} Directly working with customers, in a team, as
		well as endurance and grit to endure long tiring days.
\end{itemize}

% --- SOFT SKILLS ---
\section{SOFT SKILLS}
\begin{description}[style=multiline, leftmargin=5cm, font=\bfseries\color{TextDark}]
	\item[Critical/Logical Mind] Innovative, Fully computer literate, Complex
		problem-solving skills.
		
	\vspace{2pt}


	\item[Predictable] Fast worker, especially under pressure. Strong decision
		maker. Honest and Loyal.
		
	\vspace{2pt}


	\item[Life Long Learner] Large and wide interest span and general knowledge,
		as well as a fast learner with great long term memory
		
	\vspace{2pt}


	\item[Problem Solving] Ability to analyze complex systems and
		implement efficient solutions.
		
	\vspace{2pt}


	\item[Reliability] Consistent history of meeting deadlines and
		exceeding project requirements.
		
	\vspace{2pt}


	\item[Adaptability] Fast learner capable of pivoting between
		different programming paradigms and environments.
		
	\vspace{2pt}


	\item[Collaboration] Experienced in team work and collaborative
		development (Stellenbosch University Group Projects).
\end{description}

% --- INTERESTS ---
\section{INTERESTS}
\begin{itemize}
    \item \textbf{Simulations:} Reading up on high performance simulations and
		how they are accomplished as well as playing them. Some of these
		include: Sim racing, flight simulators, DCS ect.
		
	\vspace{2pt}


    \item \textbf{Visual FX:} The visual effects industry in general. This ties
		in with my interest in simulations as much of vfx is simulations.
	\item \textbf{STEM entertainment:} I spend my free time watching STEM
		content on platforms like YouTube and Nebula.
		
	\vspace{2pt}


	\item \textbf{Aviation and Motor Racing:} This again links to my interest in
		simulations, as I find airplanes, cars, and how they are
		represented in software and games fascinating.
		
	\vspace{2pt}


	\item \textbf{Engineering:} I like to play around in the garage with basic
		electronics, welding and wood working and have built my fair share of
		mini projects with my father at home.
\end{itemize}

\end{document}
